Invariant Representations for Noisy Speech Recognition

### 2016-10-23 paper.tex
Extend introduction, fix figures

    The main idea of this work is that instead of training a robust system,
    it is possible to train a system which will be invariant to these 
    conditions. This method of training requires the labels in the dataset
    which indicate which condition a particular recording was taken in, the 
    test data doesn't need to contain these labels. The method was proposed in
    the context of image classification in~\cite{ganin2014unsupervised} and 
    will be explained in Section~\ref{sec:gradient-reverse} and the application 
    to speech recognition is discussed
    in Section~\ref{sec:invariant-speech}. It is tightly connected to the idea
    of generative adversarial networks (GAN) proposed 
    in~\cite{goodfellow2014generative} thus we start with the discussion
    on this type of generative networks in Section~\ref{sec:gans}

    %TODO

\section{Generative Adversarial Networks}
\label{sec:gans}
    One of the most insightful recent advantages in the area of generative models
    is the models of the family of generative adversarial networks (GAN).
    A GAN consists of two networks: generator and discriminator. The generator 
    network $G$ has an
    input of randomly generated vector and is asked to produce an image 
    similar to the images in the training set. The discriminator network $D$
    can either receive a generated image from the generator $G$ or an image
    from the training set, the task of the discriminator is to distinguish
    between a generated image and a ``real'' image taken from the dataset. Thus
    the discriminator is just a classifier network with a sigmoid output
    and can be trained with the gradient methods. The main idea of the generative adversarial
    training is that it is possible to propagate the gradient of the discriminator
    network further to the generator network stacking them on top of each other.
    This leads to an efficient training procedure and GANs achieved the state of the
    art that time on handwritten digit generation MNIST dataset.

@@

In this work we focus on speech recognition using DNN-HMM hybrid systems. The
recording conditions, speaker identity, or gener might be considred to be domains
and adptation task corresponds to making the hidden layer representations be 
invariant with respect to those conditions. We hypothesize that this method of
training helps to generalize on unseen conditiions and requires only very small
amount of labeling the conditions, see Section~\ref{sec:experiments} for experimental
evaluation.

@@

\begin{figure}
    \centering
    \captionsetup[subfigure]{oneside,margin={0.3cm,0cm}}
    \begin{subfigure}[b]{0.3\linewidth}
        \centering
        \includegraphics[width=0.9\linewidth]{model.pdf}
        \caption{The model consists of three neural networks. The encoder $E$ produces
        the intermediate representation $h$ which used in the recognizer $R$ and 
        in the discriminator $D$. The hidden representation $h$ is trained to improve
        the recognition and minimize the discrimination accuracy. The discriminator
        is a classifier trained to maximize its accuracy on the gender or the noise type
        recognition task.}
        \label{fig:model}
    \end{subfigure}%
    \begin{subfigure}[b]{0.7\linewidth}
        \centering
        \includegraphics[width=\linewidth]{wer_avg.pdf}
        \includegraphics[width=\linewidth]{wer_seen_unseen.pdf}
        \caption{Up: Average performance of the model depending on the number of noise
            conditions used for training. Bottom: Average performance on seen condition versus unseen.
            Testing was performed on all wv1 conditions.
            }
        \label{fig:model}
    \end{subfigure}%
\end{figure}

@@

The results are summarized in Table~\ref{tab:results}. 
In our experiments we did not use layerwise pretraining not uncommonly used for small
datasets due to the difficulties of combining it with the invariance training. Our preliminary
experiments show that the network is not able to leave the parameter region it reaches after 
pretraining.

%\begin{figure}
%    \centering
%    \begin{subfigure}[b]{0.5\linewidth}
%        \centering
%        \includegraphics[width=\linewidth]{tsne-original.png}
%    \end{subfigure}%
%    \begin{subfigure}[b]{0.5\linewidth}
%        \centering
%        \includegraphics[width=\linewidth]{tsne-invariant.png}
%    \end{subfigure}%
%    \caption{t-SNE visualization of the last hidden layer using the clean development
%    subset. On the left, the baseline
%    model. On the right, the model trained with the adversarial objective. Colors 
%    represent genders.}
%    \label{fig:tsne}
%\end{figure}

>>>>

    The main idea of this work is that instead of training a robust system,
    it is possible to train a system which will be invariant to these 
    conditions. This method of training requires the labels in the dataset
    which indicate which condition a particular recording was taken in, the 
    test data doesn't need to contain these labels. The method was proposed in
    the context of image classification in~\cite{ganin2014unsupervised} and 
    will be explained in Section~\ref{sec:gradient-reverse} and the application 
    to speech recognition is discussed
    in Section~\ref{sec:invariant-speech}. It is tightly connected to the idea
    of generative adversarial networks (GAN) proposed 
    in~\cite{goodfellow2014generative} thus we start with the discussion
    on this type of generative networks in Section~\ref{sec:gans}, continue
    with the description of the gradient reverse method in 
    Section~\ref{sec:gradient-reverse}. Main contributions of this work
    include the development of an acoustic model benefiting from invariant
    representations constructed similarly to the gradient reverse method
    (see Section~\ref{sec:invariant-speech}); and thorough experimentation
    on a publicly available Aurora-4 dataset for noisy speech recognition 
    (see Sectibn~\ref{sec:experiments}).

\section{Generative Adversarial Networks}
\label{sec:gans}
    One of the most insightful recent advantages in the area of generative models
    is the models of the family of generative adversarial networks (GAN).
    A GAN consists of two networks: generator and discriminator. The generator 
    network $G$ has an
    input of randomly generated vector and is asked to produce an image 
    similar to the images in the training set. The discriminator network $D$
    can either receive a generated image from the generator $G$ or an image
    from the training set, the task of the discriminator is to distinguish
    between a generated image and a ``real'' image taken from the dataset. Thus
    the discriminator is just a classifier network with a sigmoid output
    and can be trained with the gradient methods. The main idea of the generative adversarial
    training is the possibility to propagate the gradient of the discriminator
    network further to the generator network stacking them on top of each other.

@@

In this work we focus on speech recognition using DNN-HMM hybrid systems. The
recording conditions, speaker identity, or gener might be considred to be domains
and adptation task corresponds to making the hidden layer representations be 
invariant with respect to those conditions. We hypothesize that this method of
training helps to generalize on unseen conditiions and requires only very small
amount of supervision -- the condition labels.

@@

\begin{figure}
    \centering
    \captionsetup[subfigure]{oneside,margin={0.3cm,0cm}}
    \begin{subfigure}[b]{0.3\linewidth}
        \centering
        \includegraphics[width=0.9\linewidth]{model.pdf}
        \caption{The model consists of three neural networks. The encoder $E$ produces
        the intermediate representation $h$ which used in the recognizer $R$ and 
        in the discriminator $D$. The hidden representation $h$ is trained to improve
        the recognition and minimize the discrimination accuracy. The discriminator
        is a classifier trained to maximize its accuracy on the gender or the noise type
        recognition task.}
        \label{fig:model}
    \end{subfigure}%
    \begin{subfigure}[b]{0.7\linewidth}
        \centering
        \includegraphics[width=\linewidth]{wer_avg.pdf}
        \includegraphics[width=\linewidth]{wer_seen_unseen.pdf}
        \caption{Up: Average performance of the model depending on the number of noise
            conditions used for training. Bottom: Average performance on seen condition versus unseen.
            Testing was performed on all wv1 conditions.
            }
        \label{fig:results}
    \end{subfigure}
    \caption{Model and results.}
\end{figure}

@@

The results are summarized in Table~\ref{tab:results}. 
In our experiments we did not use layerwise pretraining not uncommonly used for small
datasets due to the difficulties of combining it with the invariance training. Our preliminary
experiments show that the network is not able to leave the parameter region it reaches after 
pretraining. The Figure~\ref{fig:results} visualizes the average performance and the
performance on seen conditions versus unseen. We conclude that the best performance
gain can be acheived in the case of small amount of noisy samples in the training set.
